%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}
\begin{cventries}
    \vspace{-1.5 mm}
    \cventry
    {Software Engineer – Web Scraping and Security} % Job title
    {Data Impact by Nielsen IQ} % Organization
    {Paris, 75009, France} % Location
    {September 2021 - July 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilitiesDéveloppement et maintenance d'un système proxy 4G pour le web scraping.
            \item {
                        \textbf{4G System Orchestration and Scalability} \textbf{\cdotp} \textit{\textbf{Linux}, \textbf{Python}, \textbf{FastAPI}, \textbf{Docker}, \textbf{Docker Compose}, \textbf{SIM Card Networking}, \textbf{Networking}} \textbf{\cdotp} \textit{Orchestrated a robust, scalable 4G proxy system, transforming a POC into an architecture capable of managing over 1TB of data daily. Designed fault-tolerant mechanisms to handle frequent hardware errors across distributed servers. Also developed an API, services for mobile network hardware control, failure management, and logging. Acted as Level 3 support.}
                  }
            \item {
                        \textbf{Responsible for the Stability of Business Critical Spiders (data collection modules)} \textbf{\cdotp} \textit{\textbf{Python}} \textbf{\cdotp} \textit{Ensured the stability and performance of critical data-collection modules. Actively monitored performance metrics and implemented immediate fixes, contributing to the product's overall quality and reliability.}
                  }
            \item {
                        \textbf{Process Optimization through Reverse Engineering} \textbf{\cdotp} \textit{\textbf{Python}, \textbf{Chrome Dev Tools}, \textbf{JADX}, \textbf{Frida}, \textbf{Javascript}, \textbf{Go}, \textbf{Android tools}} \textbf{\cdotp} \textit{Key member of a specialized reverse engineering team focused on continuous data collection optimization. For example, identified and implemented a solution that reduced a costly spider's monthly operational costs by 97\% (6,000€).}
                  }
            \item {
                        \textbf{Session Management Middleware Development} \textbf{\cdotp} \textit{\textbf{Python}} \textbf{\cdotp} \textit{Developed a middleware layer to standardize session management, which had previously required a more advanced understanding of the framework and often resulted in hard-to-read code. The middleware abstracted IP and cookie session management, increasing code readability and reducing the potential for errors.}
                  }
            \item {
                        \textbf{Internal API and Tool Development} \textbf{\cdotp} \textit{\textbf{Python}, \textbf{Bash}, \textbf{Go}, \textbf{Java}, \textbf{Flask}} \textbf{\cdotp} \textit{Designed and implemented an array of internal APIs and services tailored to meet specific organizational needs. Notable projects include a real-time monitoring service for proxy status that also issued Slack alerts for persistent errors, and an API for request modification to imitate application behaviors.}
                  }
            \item {
                        \textbf{Industry Trend Monitoring} \textbf{\cdotp} \textit{Continuously evaluated emerging technologies and methodologies that could enhance data collection capabilities, improve internal software architecture, or address challenges the team encountered.}
                  }
        \end{cvitems}
    }

    \cventry
    {Unity Developer Intern} % Job title
    {Creo} % Organization
    {Montreal, Canada} % Location
    {August 2019 - November 2019} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {
                        \textbf{Contributed to the company's Unity assets} \textbf{\cdotp} \textit{\textbf{C\#}} \textbf{\cdotp} \textit{Contributed to the ongoing development of interactive expositions by building Unity assets.}
                  }
            \item {
                        \textit{Represented the company at an event as a technical expert, assisting participants in the creation of prototypes.}
                  }
        \end{cvitems}
    }
\end{cventries}